# {{< fa copy size=1x >}} &nbsp;&nbsp;Remove duplicates


## Detect duplicated references

Many available tools:

- Zotero & Excel - Painful
- R package [`revtools`](https://github.com/mjwestgate/revtools) - No more maintained
- R package [`synthesisr`](https://github.com/mjwestgate/synthesisr)
- R package [`bibliometrix`](https://www.bibliometrix.org/home/)
- and many more...


<br>

. . .


Let's keep it simple: 

{{< fa circle-right >}} &nbsp;The `duplicated()` function



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Easy case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change and biodiversity", 
              "Climate change and biodiversity",
              "Climate change and biodiversity",
              "Fisheries and management - Part I", 
              "Fisheries and management - Part II"))
refs
```
:::

::: {.column width=50%}
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Easy case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change and biodiversity", 
              "Climate change and biodiversity",
              "Climate change and biodiversity",
              "Fisheries and management - Part I", 
              "Fisheries and management - Part II"))
refs
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")
dups
```
:::

::: {.column width=50%}
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Easy case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change and biodiversity", 
              "Climate change and biodiversity",
              "Climate change and biodiversity",
              "Fisheries and management - Part I", 
              "Fisheries and management - Part II"))
refs
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")
dups
```

<br>

```{r}
#| echo: true
#| eval: true

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::: {.column width=50%}
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Real case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change", 
              "CLIMATE CHANGE",
              "Climate- change."))
```

<br>

:::

::: {.column}
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Real case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change", 
              "CLIMATE CHANGE",
              "Climate- change."))
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::: {.column}
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Real case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change", 
              "CLIMATE CHANGE",
              "Climate- change."))
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::: {.column}
**Clean data**

```{r}
#| echo: true
#| eval: true

# Convert to lower case ----
(titles <- tolower(refs$"title"))
```
:::

::::


## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Real case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change", 
              "CLIMATE CHANGE",
              "Climate- change."))
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::: {.column}
**Clean data**

```{r}
#| echo: true
#| eval: true

# Convert to lower case ----
(titles <- tolower(refs$"title"))
```

```{r}
#| echo: true
#| eval: true

# Remove punctuation ----
(titles <- gsub("[[:punct:]]", " ", titles))
```
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Real case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change", 
              "CLIMATE CHANGE",
              "Climate- change."))
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::: {.column}
**Clean data**

```{r}
#| echo: true
#| eval: true

# Convert to lower case ----
(titles <- tolower(refs$"title"))
```

```{r}
#| echo: true
#| eval: true

# Remove punctuation ----
(titles <- gsub("[[:punct:]]", " ", titles))
```

```{r}
#| echo: true
#| eval: true

# Remove multi-whitespace ----
(titles <- gsub("\\s+", " ", titles))
```
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Real case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change", 
              "CLIMATE CHANGE",
              "Climate- change."))
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::: {.column}
**Clean data**

```{r}
#| echo: true
#| eval: true

# Convert to lower case ----
(titles <- tolower(refs$"title"))
```

```{r}
#| echo: true
#| eval: true

# Remove punctuation ----
(titles <- gsub("[[:punct:]]", " ", titles))
```

```{r}
#| echo: true
#| eval: true

# Remove multi-whitespace ----
(titles <- gsub("\\s+", " ", titles))
```

```{r}
#| echo: true
#| eval: true

# Remove leading and trailing whitespace ----
(titles <- trimws(titles))
```
:::

::::



## The `duplicated()` function

:::: {.columns}

::: {.column width=50%}
**Real case**

```{r}
#| echo: true
#| eval: true

# Create dataset ----
refs <- data.frame(
  "title" = c("Climate change", 
              "CLIMATE CHANGE",
              "Climate- change."))
```

<br>

```{r}
#| echo: true
#| eval: true

# Detect duplicates ----
dups <- duplicated(refs$"title")

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::: {.column}
**Clean data**

```{r}
#| echo: true
#| eval: true

# Convert to lower case ----
(titles <- tolower(refs$"title"))
```

```{r}
#| echo: true
#| eval: true

# Remove punctuation ----
(titles <- gsub("[[:punct:]]", " ", titles))
```

```{r}
#| echo: true
#| eval: true

# Remove multi-whitespace ----
(titles <- gsub("\\s+", " ", titles))
```

```{r}
#| echo: true
#| eval: true

# Remove leading and trailing whitespace ----
(titles <- trimws(titles))
```

<br>

```{r}
#| echo: true
#| eval: true
# Detect duplicates ----
dups <- duplicated(titles)

# Append results ----
refs$"duplicate" <- as.numeric(dups)
refs
```
:::

::::



